---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

```{r}
data<-read.csv("activity.csv")
```

## What is mean total number of steps taken per day?

How many steps were taken per day?
```{r fig.width=7, fig.height=6}
x<-tapply(data$steps,data$date,sum)
hist(x,xlab="Number of steps/day",main="Histogram of steps/day",las=1)
```
With mean and median steps per day:
```{r mean and median}
mean(x,na.rm=T)
median(x,na.rm=T)

```


## What is the average daily activity pattern?

What interval has the highest average number of steps?

```{r fig.width=7, fig.height=6}
x<-tapply(data$steps,data$interval,mean,na.rm=T)
plot(x,xlab="Time interval",ylab="Mean number of steps",type="l",las=1)
```

```{r interval}
int<-c(1:length(x))[x==max(x)]
```
```{r time}
time<-as.numeric(names(x[x==max(x)]))
```

The maximum steps occurred during interval `r int` at time `r time`.


## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
